Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-10-02 SDSS Journal Paper/JDS supplemental items Resubmisson/JDS-Resubmisson.tex
Updates for resubmission to JDS

The large set of publicly available data (primarily from \url{data.iowa.gov}) we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. {\textcolor{blue}{The user selects a single town of interest and we add summary variables reflecting QoL metrics such as distance to local schools and city budget. Then, the user can}} in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload \citep{few}.

>>>>

The large set of publicly available data (primarily from \url{data.iowa.gov}) we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. The user selects a single town of interest and we add summary variables reflecting QoL metrics such as distance to local schools and city budget. Then, the user can in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload \citep{few}.

### 2022-10-02 SDSS Journal Paper/JDS-Resubmisson.Rmd
Updates for resubmission to JDS

The large set of publicly available data (primarily from \url{data.iowa.gov}) we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. \svp{The user selects a single town of interest and we add summary variables reflecting QoL metrics such as distance to local schools and city budget. Then, the user can} in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload [@few].

>>>>

The large set of publicly available data (primarily from \url{data.iowa.gov}) we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. The user selects a single town of interest and we add summary variables reflecting QoL metrics such as distance to local schools and city budget. Then, the user can in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload [@few].
